Depression and suicidality as costly signals of need

### 2021-04-09 Paper.rmd
change one note. Commiting to pull

# To do:
- add vignettes to SI
- mention somewhere referring to them all as signals even though we know they provide info as cues too

>>>>

# To do:
- add vignettes to SI (Mild depression = crying plus behavior change)
- mention somewhere referring to them all as signals even though we know they provide info as cues too
